%===============================================================================
% File: itr3.tex
% Description: Example LaTeX document satisfying Itr3.pdf requirements
%===============================================================================

\documentclass[12pt]{article}

%------------------------------------------------------------------------------
% PACKAGES
%------------------------------------------------------------------------------
\usepackage[margin=1in]{geometry}   % Set page margins
\usepackage{graphicx}               % Include images
\usepackage{hyperref}               % Clickable links and references
\usepackage{amsmath,amssymb}        % Math symbols if needed
\usepackage{enumitem}               % Better control over lists
\usepackage{titling}                % For a nicer title page (optional)
\usepackage{setspace}               % For spacing (optional)

%------------------------------------------------------------------------------
% TITLE & AUTHOR
%------------------------------------------------------------------------------
\title{EECS2311 -- Iteration 3: Time to Release}
\author{Team Name \\ Section Z \\ Group 12}
\date{\today}

%------------------------------------------------------------------------------
% BEGIN DOCUMENT
%------------------------------------------------------------------------------
\begin{document}
\maketitle

\tableofcontents
\newpage

%===============================================================================
% SECTION 1: Introduction / Overview
%===============================================================================
\section{Introduction and Overview}

This document is prepared for Iteration 3 of our EECS2311 Software Development Project.
It follows the instructions laid out in the \emph{Itr3.pdf} document and addresses the
process, implementation, testing, refactoring, and documentation requirements for the final release.

%===============================================================================
% SECTION 2: Revised Planning Process
%===============================================================================
\section{Revised Planning Process}

\subsection{Updated User Stories and Priorities}
Provide a summary of all user stories (both new and leftover from previous iterations),
along with their updated priorities and cost estimates.

\subsection{Velocity and Sprint Planning}
Discuss your estimated velocity based on the progress from Iteration 2.
Explain how you accounted for additional tasks such as refactoring and testing,
and how you reallocated your resources for Itr3.

\subsection{Discrepancies from Original Plan}
Include the original plan (from Itr2) and highlight any changes here.
Briefly justify why these changes were necessary.

%===============================================================================
% SECTION 3: Implementation, Testing, and Bug Fixing
%===============================================================================
\section{Implementation, Testing, and Bug Fixing}

\subsection{Implemented Features}
List the user stories implemented in this iteration. Each user story should be
fully functional with proper unit tests, integration tests, and a working UI.

\subsection{Testing Approach}
Describe how you tested the new features and how you addressed previously
reported bugs. Mention the specific frameworks/tools used (e.g., JUnit, PyTest, etc.).
Refer to any relevant test logs or code coverage reports here.

\subsection{Bug Fixes}
Explain the critical bugs that were identified and fixed. Reference any
GitHub Issue IDs, how you resolved them, and whether any remain outstanding.

%===============================================================================
% SECTION 4: Refactoring
%===============================================================================
\section{Refactoring and Code Smell Resolutions}

\subsection{Identified Code Smells / Design Issues}
List the code smells or design issues you discovered. For each,
provide a short before/after snapshot of your design if possible.

\subsection{Refactoring Techniques Applied}
For each significant refactoring, describe:
\begin{itemize}
    \item \textbf{What was changed} (e.g., introduced new classes, replaced primitive types with objects)
    \item \textbf{Why it was changed} (e.g., to improve maintainability, readability, testability)
    \item \textbf{How it improves the system} (link to relevant design principles)
\end{itemize}

\subsection{Outstanding Issues}
If there are known issues you have chosen not to fix this iteration,
explain the rationale and future plan for addressing them.

%===============================================================================
% SECTION 5: Documentation Updates
%===============================================================================
%===============================================================================
% SECTION 5: Documentation Updates
%===============================================================================
\section{Documentation Updates}

\subsection{Wiki / README Changes}
Summarize any major changes made in your GitHub Wiki or README to reflect
Iteration 3 updates. This includes new instructions for how to install, run,
and test your application.

\subsection{Project Repository}
The project repository can be found at the following URL:
\url{https://github.com/victobui/EECS-2311-Final-Project-Salon-AI}

\subsection{Architecture Diagram}
Include or describe any architecture changes here. Label each seam in
the diagram with the corresponding integration test classes or modules.

%===============================================================================
% SECTION 6: Submission and Evaluation
%===============================================================================
\section{Submission and Evaluation}

According to \emph{Itr3.pdf}, the final submission must include:
\begin{itemize}
    \item Source code with proper structure (\texttt{src/}, \texttt{test/}, \texttt{lib/}, etc.).
    \item Database folder if your application needs it.
    \item Documents such as:
    \begin{itemize}
        \item Old planning document (from Itr2).
        \item This updated Iteration 3 plan.
        \item A refactoring document or incorporate that content here.
        \item Revised architecture diagram.
    \end{itemize}
    \item Log file containing meeting minutes, rationale for changes, big design decisions, etc.
\end{itemize}

Include everything in your GitHub repository by the deadline. Ensure it is straightforward to compile, run, and test your code on a fresh machine.

%===============================================================================
% SECTION 7: Conclusion
%===============================================================================
\section{Conclusion}

In this document, we presented the updated plan, implemented features, refactoring steps,
and documentation for Iteration 3. We have accounted for the guidelines in
\emph{Itr3.pdf} and prepared the project for final release.

%===============================================================================
% BIBLIOGRAPHY (OPTIONAL)
%===============================================================================
% If you have references, uncomment the lines below and update refs.bib accordingly.
% \bibliographystyle{plain}
% \bibliography{refs}

\end{document}
